### 2021-04-20 preliminaries.tex
what is a proof?
KBO and a precedence as a permutation

Given a problem $P$ in \gls{cnf},
a \emph{saturation-based} \gls{atp} searches for a refutational proof
by iteratively applying the \emph{inference rules} from the given \emph{calculus}
to infer new clauses entailed by $\mathit{Cl}$.
As soon as the empty clause, denoted by $\square$, is inferred,
the prover concludes that the premises entail the conjecture.
The sequence of inferences taken in the proof search constitutes a proof.
In case the premises do not entail the conjecture,
the proof search continues until
the set of the inferred clauses is saturated with respect to the inference rules.
In the common setting of time-restricted proof search, a time limit may end the process prematurely.

@@

The \emph{\acrfull{kbo}} \cite{Knuth1983}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation of the non-logical symbols of the input problem.
In this work we focus on the task of finding a symbol precedence which
leads to a good performance of an ATP
when plugged into the \gls{kbo},
leaving all the symbol weights at the default 
value 1 as set by the \gls{atp} \Vampire{}.

>>>>

Given a problem $P$ in \gls{cnf},
a \emph{saturation-based} \gls{atp} searches for a refutational proof
by iteratively applying the \emph{inference rules} from the given \emph{calculus}
to infer new clauses entailed by $\mathit{Cl}$.
As soon as the empty clause, denoted by $\square$, is inferred,
the prover concludes that the premises entail the conjecture.
The sequence of those inferences leading up from the input clauses $\mathit{Cl}$ to the discovered $\square$ constitutes a proof.
In case the premises do not entail the conjecture,
the proof search continues until
the set of the inferred clauses is saturated with respect to the inference rules.
In the common setting of time-restricted proof search, a time limit may end the process prematurely.

@@

The \emph{\acrfull{kbo}} \cite{Knuth1983}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation\footnote{
The definition of KBO does not require the precedence to be total. 
However, for the use in ATPs, the more symbols and thus also terms 
we can compare, the better. % That is why we define a precedence as a permutation.
} of the non-logical symbols of the input problem.
In this work we focus on the task of finding a symbol precedence which
leads to a good performance of an ATP
when plugged into the \gls{kbo},
leaving all the symbol weights at the default 
value 1 as set by the \gls{atp} \Vampire{}.
